\package{}: an \R{} package for implemetation of the ITHIM model

### 2016-09-12 manuscript/manuscript.tex
Added symbolic link to manuscript/figures/
Edits to manuscript 1

\newcommand{\col}[2][red]{\textcolor{#1}{#2}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\package}{\emph{ITHIM}}
\newcommand{\compendium}{\emph{ReadSimCompendium}}
\newcommand{\ithim}{\emph{ITHIM}}
\renewcommand{\bowtie}{\emph{bowtie}}
\newcommand{\ebseq}{\emph{EBSeq}}
\newcommand{\deseq}{\emph{DESeq2}}
\newcommand{\R}{\emph{R}}
\newcommand{\rnaseq}{RNA-seq}
\newcommand{\gi}{gene/isoform}
\newcommand{\gis}{genes/isoforms}
\newcommand{\pest}{\texttt{ParamEstimation}}
\newcommand{\csimu}{\texttt{CountSimu}}
\newcommand{\writeRSEM}{\texttt{writeRSEMFiles}}
\newcommand{\sgy}[1]{{\itshape\col{#1}}}
\newcommand{\XX}{\sgy{XX}}

@@

\section{Summary:}

@@

\section{Availability:}
The source code and data files for \package{} are publicly available
on GitHub at \url{https://github.com/syounkin/ITHIM}.

\url{http://www.ithim.ghi.wisc.edu}.

\section{Contact:}
\href{patz@wisc.edu}{patz@wisc.edu}
\end{abstract}

\section{Introduction}

ITHIM is a mathematical model that integrates data on travel patterns,
physical activity, fine particulate matter, GHG emissions, and disease
and injuries. Based on population and travel scenarios. The model has
been used to calculate the health impacts of walking and bicycling
short distances usually traveled by car or driving low-emission
automobiles \cite{woodcock2013}.

\begin{methods}
\section{Method}

\begin{itemize}
\item NHTS data
\item GBD data
\item ITHIM model parameters
\end{itemize}

@@

\section{Regional Example}

@@

\begin{figure}[t]
    \centerline{\includegraphics[width=0.4\textwidth]{./figures/hhsmap}}\centerline{\includegraphics[width=0.4\textwidth]{./figures/ITHIMObjs-2}}
    \caption{Change in total national DALYs for each regional transportation
estimates.
}\label{dalyFigure}
\end{figure}

\section*{Acknowledgment}

\paragraph{Funding\textcolon} SGY is supported by$\ldots$ , JV, JP, $\ldots$

%\bibliographystyle{natbib}
%\bibliographystyle{bmc_article}
\bibliographystyle{mypapers}
\bibliography{ITHIM}
\end{document}

>>>>

\newcommand{\col}[2][red]{\textcolor{#1}{#2}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\package}{\emph{ITHIM}}
\newcommand{\ithim}{\emph{ITHIM}}
\newcommand{\R}{\emph{R}}
\newcommand{\sgy}[1]{{\itshape\col{#1}}}
\newcommand{\XX}{\sgy{XX}}
\newcommand{\webpage}{\url{http://www.ithim.ghi.wisc.edu}}

@@

\section{Summary:}
We divided the U.S. metropolitan regions into 10 regions defined by
the Department of Health and Human Services (HHS1-10).  We performed a
comparative risk analysis for each of the regions using national
averages as the baseline.  We investigated the active transport
component of the ITHIM model by estimating regional travel parameters
using the National Household Transportation Survey.  The West coast
and the Northeast of the U.S. have travel patterns that, if mirrored
by the nation, would save the U.S. thousands to hundreds of thousands
DALYs.

\section{Availability:}
\package{} may be explored using the user interface avaiable
at \webpage{}.  The source code and data files for \package{} are
publicly available on GitHub at \webpage{}.

See \webpage{} for links to the source code, manual, tutorial and
links for more information about the ITHIM model.

\section{Contact:}
\href{javargo@wisc.edu}{javargo@wisc.edu}
\end{abstract}

\section{Introduction}
ITHIM is a statistical model that integrates data on travel patterns,
physical activity, fine particulate matter, GHG emissions, and disease
and injuries. Based on population and travel scenarios. The model has
been used to calculate the health impacts of walking and bicycling
short distances usually traveled by car or driving low-emission
automobiles \cite{woodcock2013}.

Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do
eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad
minim veniam, quis nostrud exercitation ullamco laboris nisi ut
aliquip ex ea commodo consequat. Duis aute irure dolor in
reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla
pariatur. Excepteur sint occaecat cupidatat non proident, sunt in
culpa qui officia deserunt mollit anim id est laborum. Lorem ipsum
dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor
incididunt ut labore et dolore magna aliqua.

Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do
eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad
minim veniam, quis nostrud exercitation ullamco laboris nisi ut
aliquip ex ea commodo consequat. Duis aute irure dolor in
reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla
pariatur. Excepteur sint occaecat cupidatat non proident, sunt in
culpa qui officia deserunt mollit anim id est laborum.

\begin{methods}
\section{Methods}
\begin{itemize}
\item The coefficient of variation was fixed at ??? for all models.
  Earlier ITHIM models estimated this as a function of total active
  tranpsort time to model the decrease in variance of active transport
  time that occurs for increasing means, i.e., fitter communities have
  less variance in active transport time.
\item The mean non-travel activity for the referent group was modeled
  as a variable.  The relative means across age-sex strata were fixed,
  and estimated using ATUS.
\item The national DALYs were stimated using the attributable fraction
  provided by the comparitive risk assesment.  The estimates for
  disease burned came from WHO and their GBD study.
\item Not all of the regions had the same sample size.  In fact a few
  of the regions have relativel low sample size.  Maybe we should put
  confidence intervals on our estimates.
\end{itemize}

@@

@@

\section{Regional Example}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do
eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad
minim veniam, quis nostrud exercitation ullamco laboris nisi ut
aliquip ex ea commodo consequat. Duis aute irure dolor in
reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla
pariatur. Excepteur sint occaecat cupidatat non proident, sunt in
culpa qui officia deserunt mollit anim id est laborum. Lorem ipsum
dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor
incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea
commodo consequat. Duis aute irure dolor in reprehenderit in voluptate
velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint
occaecat cupidatat non proident, sunt in culpa qui officia deserunt
mollit anim id est laborum. Lorem ipsum dolor sit amet, consectetur
adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore
magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation
ullamco laboris nisi ut aliquip ex ea commodo consequat.

@@

\begin{figure}[t]
    \centerline{\includegraphics[width=0.4\textwidth]{./figures/hhsmap}}\centerline{\includegraphics[width=0.4\textwidth]{./figures/fig2}}
    \caption{Change in total national DALYs for each regional transportation
estimates.
}\label{dalyFigure}
\end{figure}

\section*{Acknowledgment}
\paragraph{Funding\textcolon} SGY is supported by$\ldots$ , JV, JP, $\ldots$

\bibliographystyle{natbib}
%\bibliographystyle{bmc_article}
%\bibliographystyle{mypapers}
\bibliography{ITHIM}
\end{document}
